Estimating individual subjective values of emotion regulation strategies

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added pilot files
changed variable names

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","Workspace_ERED.RData"))

@@

`r afex::nice(SubjArousalView_aov) %>% knitr::kable(x = .)` 
$BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```
## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjArousalReg_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjArousalReg_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```
## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
*Corrugator*:
ANOVA: 
`r afex::nice(EMGCorrView_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGCorrView_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrView_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
*Levator*:
ANOVA: 
`r afex::nice(EMGLevView_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGLevView_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevView_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figures:
```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

@@

print(FigEMGLevViewPilot)
```
## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
*Corrugator*:
ANOVA: 
`r afex::nice(EMGCorrReg_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGCorrReg_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrReg_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
*Levator*:
ANOVA: 
`r afex::nice(EMGLevReg_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGLevReg_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevReg_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figures:
```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

@@

print(FigEMGLevRegPilot)
```
## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjEffort_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjEffort_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

>>>>

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","Workspace_ERED_pilot.RData"))

@@

`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` 
$BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```
## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```
## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
*Corrugator*:
ANOVA: 
`r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
*Levator*:
ANOVA: 
`r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGLevView__pilotBF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figures:
```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

@@

print(FigEMGLevViewPilot)
```
## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
*Corrugator*:
ANOVA: 
`r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
*Levator*:
ANOVA: 
`r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figures:
```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

@@

print(FigEMGLevRegPilot)
```
## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}
